---
title: "dissertation data from mturk round 3"
output: github_document
---
## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. 
When you click the **Knit** button all R code chunks are run and a markdown file 
(.md) suitable for publishing to GitHub is generated.

## Setup 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(stdmod)      # for computing the standardized moderation effect conveniently
library(lavaan)      # for doing path analysis in lavaan
library(semTools)    # for HTMT heterotrait monotrait ratio
library(ltm)         # for Cronbach's alpha
library(psych)       # for summary tables
library(dplyr)       # for simple counts
library(freqtables)  # for frequency tables

setwd("C:/Users/pwcol/OneDrive/Documents/Academics/Shoja-dissertation-prep-spring2023")
mturk_round_3 <- read.csv("mturk-round-3-r-import.csv")
mturk_round_3 <- mturk_round_3[-320, ]
```

## CFA full 
```{r CFA}
cfa_model <- "
THP =~ THP_01 + THP_02 + THP_03 + THP_04 + THP_05 + THP_06 + THP_07 + THP_08 + THP_09
SLB =~ SLB_01 + SLB_02 + SLB_03 + SLB_04 + SLB_05 + SLB_06 + SLB_07 
TL =~ TL_01 + TL_02 + TL_03 + TL_04 + TL_05 + TL_06 + TL_07 + TL_08 + TL_09 + TL_10
TT =~ TT_01 + TT_02 + TT_03 + TT_04 + TT_05 + TT_06 + TT_07 + TT_08 + TT_09 + TT_10
TC =~ TC_02 + TC_03 + TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_01 + TSC_02 + TSC_03 + TSC_04 + TSC_05 + TSC_06 + TSC_07 + TSC_08 + TSC_09 
        + TSC_10 + TSC_11 + TSC_12 + TSC_13 + TSC_14 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07
  "
cfa_results <- cfa(model = cfa_model, data = mturk_round_3)
summary(cfa_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(cfa_results, "cor.lv")

```
## Cronbach a: all items

```{r}
# Calculate Cronbach's Alpha for all items 

print("Cronbach's Alpha for all THP Team Performance")
cronbach.alpha(mturk_round_3[1:319 ,
                             c('THP_01','THP_02','THP_03','THP_04','THP_05','THP_06','THP_07','THP_08','THP_09')])

print("Cronbach's Alpha for all SLB Servant Leadership Behaviors")
cronbach.alpha(mturk_round_3[1:319 , 
                             c('SLB_01','SLB_02','SLB_03','SLB_04','SLB_05','SLB_06','SLB_07')])

print("Cronbach's Alpha for all TL Trust in Leader")
cronbach.alpha(mturk_round_3[1:319 , 
                             c('TL_01','TL_02','TL_03','TL_04','TL_05','TL_06','TL_07','TL_08','TL_09','TL_10')])

print("Cronbach's Alpha for all TT Trust in Team")
cronbach.alpha(mturk_round_3[1:319 ,
                             c('TT_01','TT_02','TT_03','TT_04','TT_05','TT_06','TT_07','TT_08','TT_09','TT_10')])

print("Cronbach's Alpha for all TC Team Cohesion")
cronbach.alpha(mturk_round_3[1:319 , c('TC_02','TC_03','TC_04','TC_05','TC_07','TC_08')])

print("Cronbach's Alpha for all TSC Team Service Culture")
cronbach.alpha(mturk_round_3[1:319 , 
                             c('TSC_01','TSC_02','TSC_03','TSC_04','TSC_05','TSC_06','TSC_07','TSC_08','TSC_09',
                               'TSC_10','TSC_11','TSC_12','TSC_13','TSC_14','TSC_15','TSC_16')])

print("Cronbach's Alpha for all TP Team Purpose")
cronbach.alpha(mturk_round_3[1:319 , c('TP_03','TP_04','TP_05','TP_06','TP_07')])



```
## CFA net (retained items)
```{r CFA}
cfa_model <- "
THP =~ THP_01 + THP_02 + THP_04 + THP_05 + THP_06 + THP_07 + THP_09
SLB =~ SLB_02 + SLB_03 + SLB_04 + SLB_05 
TL =~ TL_02 + TL_06 + TL_08 + TL_10
TT =~ TT_02 + TT_04 + TT_06 + TT_08 + TT_10
TC =~ TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_02 + TSC_03 + TSC_05 + TSC_09 + TSC_11 + TSC_12 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07
TL_02 ~~ TT_02
THP_05 ~~ THP_06
SLB_03 ~~ SLB_05
TT_06 ~~ TT_10
TT_04 ~~ TSC_05
TP_04 ~~ TP_05
THP_04 ~~ THP_05
TC_05 ~~ TC_08
TC_04 ~~ TSC_15
THP_02 ~~ TSC_02
TSC_03 ~~ TSC_05
TL_08 ~~ TT_08
THP_01 ~~ TT_02
SLB_03 ~~ TSC_03
TT_02 ~~ TT_04
THP_07 ~~ THP_09
THP_01 ~~ THP_04
TSC_12 ~~ TSC_16
TP_03 ~~ TP_07
TP_04 ~~ TP_06
SLB_03 ~~ TSC_02
TC_04 ~~ TC_07
TC_08 ~~ TSC_02
TC_04 ~~ TSC_11
TC_07 ~~ TP_03
THP_06 ~~ SLB_03
THP_05 ~~ SLB_02
THP_09 ~~ TL_10
TSC_11 ~~ TSC_12

  "
cfa_results <- cfa(model = cfa_model, data = mturk_round_3)
summary(cfa_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(cfa_results, "cor.lv")

```

## CFA model indices 
```{r} 
# this line reports suggestions for allowing error correlation between two items  
modindices(cfa_results, sort = TRUE, maximum.number = 25)

```


## Cronbach a: retained items

```{r}
# Calculate Cronbach's Alpha for retained items  

print("Cronbach's Alpha for retained THP Team Performance")
cronbach.alpha(mturk_round_3[1:319 ,
                             c('THP_01','THP_02','THP_04','THP_05','THP_06','THP_07','THP_09')])

print("Cronbach's Alpha for retained SLB Servant Leadership Behaviors")
cronbach.alpha(mturk_round_3[1:319 , 
                             c('SLB_02','SLB_03','SLB_04','SLB_05')])

print("Cronbach's Alpha for retained TL Trust in Leader")
cronbach.alpha(mturk_round_3[1:319 , 
                             c('TL_02','TL_06','TL_08','TL_10')])

print("Cronbach's Alpha for retained TT Trust in Team")
cronbach.alpha(mturk_round_3[1:319 ,
                             c('TT_02','TT_04','TT_06','TT_08','TT_10')])

print("Cronbach's Alpha for retained TC Team Cohesion")
cronbach.alpha(mturk_round_3[1:319 , c('TC_04','TC_05','TC_07','TC_08')])

print("Cronbach's Alpha for retained TSC Team Service Culture")
cronbach.alpha(mturk_round_3[1:319 , 
                             c('TSC_02','TSC_03','TSC_05','TSC_09','TSC_11','TSC_12','TSC_15','TSC_16')])

print("Cronbach's Alpha for retained TP Team Purpose")
cronbach.alpha(mturk_round_3[1:319 , c('TP_03','TP_04','TP_05','TP_06','TP_07')])



```


## SEM full 
Standardized Moderation Effect in a Path Model by stdmod_lavaan()
From https://cran.r-project.org/web/packages/stdmod/vignettes/stdmod_lavaan.html
full model just to see what happens
mediator is TSC with 4 antecedent IVs
moderator is TSO attenuating the effect of mediator TSC on dependent variable THP

```{r SEM full}
std_model_full <- "
THP =~ THP_01 + THP_02 + THP_03 + THP_04 + THP_05 + THP_06 + THP_07 + THP_08 + THP_09
SLB =~ SLB_01 + SLB_02 + SLB_03 + SLB_04 + SLB_05 + SLB_06 + SLB_07 
TL =~ TL_01 + TL_02 + TL_03 + TL_04 + TL_05 + TL_06 + TL_07 + TL_08 + TL_09 + TL_10
TT =~ TT_01 + TT_02 + TT_03 + TT_04 + TT_05 + TT_06 + TT_07 + TT_08 + TT_09 + TT_10
TC =~ TC_02 + TC_03 + TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_01 + TSC_02 + TSC_03 + TSC_04 + TSC_05 + TSC_06 + TSC_07 + TSC_08 + TSC_09 
        + TSC_10 + TSC_11 + TSC_12 + TSC_13 + TSC_14 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07

TSC ~ SLB + TL + TT + TC
THP ~ TSC + TP + TSO_01 + TSC*TSO_01 + TS_01 
  "
std_model_full_results <- sem(std_model_full, mturk_round_3, fixed.x = FALSE)
summary(std_model_full_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(std_model_full_results, "cor.lv") 

```

## SEM net (1 interaction) 
Standardized Moderation Effect in a Path Model by stdmod_lavaan()
From https://cran.r-project.org/web/packages/stdmod/vignettes/stdmod_lavaan.html
in round 1, we removed TL trust in leader and TT trust in team 
dependent variable THP
mediator is TSC with 4 antecedent IVs
moderator is TSO attenuating the effect of mediator TSC on dependent variable THP
round 2 post-EFA items with std.all cutoff < 0.6 are in the SEM results below

```{r SEM net}
std_model_net <- "
THP =~ THP_01 + THP_02 + THP_04 + THP_05 + THP_06 + THP_07 + THP_09
SLB =~ SLB_02 + SLB_03 + SLB_04 + SLB_05 
TL =~ TL_02 + TL_06 + TL_08 + TL_10
TT =~ TT_02 + TT_04 + TT_06 + TT_08 + TT_10
TC =~ TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_02 + TSC_03 + TSC_05 + TSC_09 + TSC_11 + TSC_12 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07

TL_02 ~~ TT_02
THP_05 ~~ THP_06
SLB_03 ~~ SLB_05
TT_06 ~~ TT_10
TT_04 ~~ TSC_05
TP_04 ~~ TP_05
THP_04 ~~ THP_05
TC_05 ~~ TC_08
TC_04 ~~ TSC_15
THP_02 ~~ TSC_02
TSC_03 ~~ TSC_05
TL_08 ~~ TT_08
THP_01 ~~ TT_02
SLB_03 ~~ TSC_03
TT_02 ~~ TT_04
THP_07 ~~ THP_09
THP_01 ~~ THP_04
TSC_12 ~~ TSC_16
TP_03 ~~ TP_07
TP_04 ~~ TP_06
SLB_03 ~~ TSC_02
TC_04 ~~ TC_07
TC_08 ~~ TSC_02
TC_04 ~~ TSC_11
TC_07 ~~ TP_03
THP_06 ~~ SLB_03
THP_05 ~~ SLB_02
THP_09 ~~ TL_10
TSC_11 ~~ TSC_12

TSC ~ SLB + TL + TT + TC
THP ~ TSC + TP + TSO_01 + TSC*TSO_01 + TS_01 

  "
std_model_net_results <- sem(std_model_net, mturk_round_3, fixed.x = FALSE)
summary(std_model_net_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(std_model_net_results, "cor.lv")

```


## HTMT example
```{r}
# view the example data
HolzingerSwineford1939

# model + data setup 
HS.model <- ' visual  =~ x1 + x2 + x3
              textual =~ x4 + x5 + x6
              speed   =~ x7 + x8 + x9 '

dat <- HolzingerSwineford1939[, paste0("x", 1:9)]
htmt(HS.model, dat)

## save covariance matrix
HS.cov <- cov(HolzingerSwineford1939[, paste0("x", 1:9)])
## HTMT using arithmetic mean
htmt(HS.model, sample.cov = HS.cov, htmt2 = FALSE)
```


## HTMT
```{r}
# set up model + data in the htmt object
htmt(std_model_net, mturk_round_3)

## save covariance matrix
mturk_cov <- cov(mturk_round_3)

## create HTMT matrix using arithmetic mean
htmt(std_model_net, sample.cov = mturk_cov, htmt2 = FALSE)

```


## VIF 
1. Create a dummy variable
2. Regress the dummy variable against the independent variables
3. Estimate the VIFs

```{r}

#dummy <- rbinom(nrow(mturk_round_3), 1, 0.5)
#vif_model <- lm(std_model_net_results, data = mturk_round_3)
vif(std_model_net_results)

```


## SEM net (2 interactions) 
Standardized Moderation Effect in a Path Model by stdmod_lavaan()
From https://cran.r-project.org/web/packages/stdmod/vignettes/stdmod_lavaan.html
in round 1, we removed TL trust in leader and TT trust in team 
dependent variable THP
mediator is TSC with 4 antecedent IVs
moderator is TSO attenuating the effect of mediator TSC on dependent variable THP
round 2 post-EFA items with std.all cutoff < 0.6 are in the SEM results below

```{r SEM net with TSC*TP interaction}
std_model_net_interact <- "
THP =~ THP_01 + THP_02 + THP_04 + THP_05 + THP_06 + THP_07 + THP_09
SLB =~ SLB_02 + SLB_03 + SLB_04 + SLB_05 
TL =~ TL_02 + TL_06 + TL_08 + TL_10
TT =~ TT_02 + TT_04 + TT_06 + TT_08 + TT_10
TC =~ TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_02 + TSC_03 + TSC_05 + TSC_09 + TSC_11 + TSC_12 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07

TSC ~ SLB + TL + TT + TC
THP ~ TSC + TP + TP*TSC + TSO_01 + TSO_01*TSC + TS_01 

  "
std_model_net_interact_results <- sem(std_model_net_interact, mturk_round_3, fixed.x = FALSE)
summary(std_model_net_interact_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(std_model_net_interact_results, "cor.lv")

```


## Robustness check setup
THP ~ TSC + TP + TSC*TP + TSO_01 + TSC*TSO_01 + TS_01 
and create two new variable to replace the line above 
aggregate TSC, TP so we use average in the model and subtract the value from mean to make it mean-centered
don't need standard error for mean-centered subtract the value from the mean

1. create a new variable avg_TSC equal to the sum of all items divided by 8 (avg_TSC)
2. calculate the mean of avg_TSC and subtract this from avg_TSC on each obs. to create mean_centered_avg_TSC
3. repeat for TP

```{r}
mturk_round_3$avg_TSC <- rowSums(mturk_round_3[,c("TSC_02", "TSC_03", "TSC_05", 
                                                  "TSC_09", "TSC_11", "TSC_12", "TSC_15", "TSC_16")]) / 8

mturk_round_3$mean_centered_avg_TSC <- mturk_round_3$avg_TSC - mean(mturk_round_3$avg_TSC)

mturk_round_3$avg_TP <- rowSums(mturk_round_3[,c("TP_03", "TP_04", "TP_05", 
                                                  "TP_06", "TP_07")]) / 5

mturk_round_3$mean_centered_avg_TP <- mturk_round_3$avg_TP - mean(mturk_round_3$avg_TP)

```


## SEM net (new interaction term)
4. multiply mean centered avg TSC with mean centered avg TP to create the new interaction term
5. then test TP*TSC to see whether there is any difference

```{r SEM net}
std_model_net <- "
THP =~ THP_01 + THP_02 + THP_04 + THP_05 + THP_06 + THP_07 + THP_09
SLB =~ SLB_02 + SLB_03 + SLB_04 + SLB_05 
TL =~ TL_02 + TL_06 + TL_08 + TL_10
TT =~ TT_02 + TT_04 + TT_06 + TT_08 + TT_10
TC =~ TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_02 + TSC_03 + TSC_05 + TSC_09 + TSC_11 + TSC_12 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07

TSC ~ SLB + TL + TT + TC
THP ~ TSC + TP + mean_centered_avg_TSC*mean_centered_avg_TP + TSO_01 + TSC*TSO_01 + TS_01 
  "
std_model_net_results <- sem(std_model_net, mturk_round_3, fixed.x = FALSE)
summary(std_model_net_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(std_model_net_results, "cor.lv")

```


```{r}

```



## SEM + CTRL vars (1 interaction) 
Standardized Moderation Effect in a Path Model by stdmod_lavaan()
From https://cran.r-project.org/web/packages/stdmod/vignettes/stdmod_lavaan.html
in round 1, we removed TL trust in leader and TT trust in team 
dependent variable THP
mediator is TSC with 4 antecedent IVs
moderator is TSO attenuating the effect of mediator TSC on dependent variable THP
round 2 post-EFA items with std.all cutoff < 0.6 are in the SEM results below

```{r SEM net + CTRL vars (1 interaction) }
std_model_net <- "
THP =~ THP_01 + THP_02 + THP_04 + THP_05 + THP_06 + THP_07 + THP_09
SLB =~ SLB_02 + SLB_03 + SLB_04 + SLB_05 
TL =~ TL_02 + TL_06 + TL_08 + TL_10
TT =~ TT_02 + TT_04 + TT_06 + TT_08 + TT_10
TC =~ TC_04 + TC_05 + TC_07 + TC_08
TSC =~ TSC_02 + TSC_03 + TSC_05 + TSC_09 + TSC_11 + TSC_12 + TSC_15 + TSC_16
TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07

TSC ~ SLB + TL + TT + TC + ORG_VIRTUAL
THP ~ TSC + TP + TSO_01 + TSC*TSO_01 + TS_01
  "
std_model_net_results <- sem(std_model_net, mturk_round_3, fixed.x = FALSE)
summary(std_model_net_results, standardized = TRUE, fit.measures = TRUE, ci=TRUE)
lavInspect(std_model_net_results, "cor.lv")

```


## Descriptives
ORG_VIRTUAL
DURATION
EXP_TOTAL
EXP_MEMBER
EXP_LEADER
EXP_INDUSTRY
AGE
CAT_INDUSTRY
CAT_PURPOSE
CAT_FORMING
CAT_LEADER

```{r Descriptives}
summary(mturk_round_3[1-399,c('ORG_VIRTUAL',
                              'DURATION','EXP_TOTAL','EXP_MEMBER','EXP_LEADER',
                              'EXP_INDUSTRY','AGE')])

```

Note the full measurement model:
    THP =~ THP_01 + THP_02 + THP_03 + THP_04 + THP_05 + THP_06 + THP_07 + THP_08 + THP_09
    SLB =~ SLB_01 + SLB_02 + SLB_03 + SLB_04 + SLB_05 + SLB_06 + SLB_07 
    TL =~ TL_01 + TL_02 + TL_03 + TL_04 + TL_05 + TL_06 + TL_07 + TL_08 + TL_09 + TL_10
    TT =~ TT_01 + TT_02 + TT_03 + TT_04 + TT_05 + TT_06 + TT_07 + TT_08 + TT_09 + TT_10
    TC =~ TC_02 + TC_03 + TC_04 + TC_05 + TC_07 + TC_08
    TSC =~ TSC_01 + TSC_02 + TSC_03 + TSC_04 + TSC_05 + TSC_06 + TSC_07 + TSC_08 + TSC_09 
            + TSC_10 + TSC_11 + TSC_12 + TSC_13 + TSC_14 + TSC_15 + TSC_16
    TP =~ TP_03 + TP_04 + TP_05 + TP_06 + TP_07
    
    TSC ~ SLB + TL + TT + TC
    THP ~ TSC + TP + TSO_01 + TSC*TSO_01 + TS_01 
    
    
Note the measurement model items
    'THP_01','THP_02','THP_03','THP_04','THP_05','THP_06','THP_07','THP_08','THP_09'
    'SLB_01','SLB_02','SLB_03','SLB_04','SLB_05','SLB_06','SLB_07'
    'TL_01','TL_02','TL_03','TL_04','TL_05','TL_06','TL_07','TL_08','TL_09','TL_10'
    'TT_01','TT_02','TT_03','TT_04','TT_05','TT_06','TT_07','TT_08','TT_09','TT_10'
    'TC_02','TC_03','TC_04','TC_05','TC_07','TC_08'
    'TSC_01','TSC_02','TSC_03','TSC_04','TSC_05','TSC_06','TSC_07','TSC_08','TSC_09',
    'TSC_10','TSC_11','TSC_12','TSC_13','TSC_14','TSC_15','TSC_16'
    'TP_03','TP_04','TP_05','TP_06','TP_07'
    'TSO_01'
    'TS_01'


Note the control variables with numeric values:
    'ORG_VIRTUAL','EXP_TOTAL','EXP_MEMBER','EXP_LEADER','EXP_INDUSTRY','AGE'
    

Note the control variable with continuous values:
    'DURATION'


Note the control variables with discrete / categorical values:
    'CAT_INDUSTRY','CAT_PURPOSE','CAT_FORMING','CAT_LEADER'


```{r SEM new chunk}
df <- (mturk_round_3[,c('ORG_VIRTUAL','DURATION','EXP_TOTAL','EXP_MEMBER',
                        'EXP_LEADER','EXP_INDUSTRY','AGE','CAT_INDUSTRY',
                        'CAT_PURPOSE','CAT_FORMING','CAT_LEADER')])

#create summary table
#describe(df)

#count(df, ORG_VIRTUAL, name='Count', .drop=FALSE)
freq_table(df, ORG_VIRTUAL)
freq_table(df, EXP_TOTAL)
freq_table(df, EXP_MEMBER)
freq_table(df, EXP_LEADER)
freq_table(df, EXP_INDUSTRY)
freq_table(df, AGE)
freq_table(df, CAT_INDUSTRY)
freq_table(df, CAT_PURPOSE)
freq_table(df, CAT_FORMING)
freq_table(df, CAT_LEADER)


#'THP_01','THP_02','THP_03','THP_04','THP_05','THP_06','THP_07','THP_08','THP_09'
#'SLB_01','SLB_02','SLB_03','SLB_04','SLB_05','SLB_06','SLB_07'
#'TL_01','TL_02','TL_03','TL_04','TL_05','TL_06','TL_07','TL_08','TL_09','TL_10'
#'TT_01','TT_02','TT_03','TT_04','TT_05','TT_06','TT_07','TT_08','TT_09','TT_10'
#'TC_02','TC_03','TC_04','TC_05','TC_07','TC_08'
#'TSC_01','TSC_02','TSC_03','TSC_04','TSC_05','TSC_06','TSC_07','TSC_08','TSC_09',
#  'TSC_10','TSC_11','TSC_12','TSC_13','TSC_14','TSC_15','TSC_16'
#'TP_03','TP_04','TP_05','TP_06','TP_07'
#TSO_01
#TS_01

#create summary table, grouped by a specific variable
#describeBy(mturk_round_3, group=mturk_round_3$ORG_VIRTUAL)

```



```{r SEM new chunk}

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent 
printing of the R code that generated the plot.
